
\begin{center}
\addsec{\textsc{\textbf{Little Compline}}}
\end{center}

%\hangindent=10mm
%\hangafter=1
\begin{hang}
\noindent\makebox[\indt][l]{Priest:}Blessed is our God, always, now and ever 
and unto ages of ages.

\end{hang}

\noindent
\textcolor{red}{\textit{The reader stands in the middle of the chapel.}}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}Amen. Glory to Thee, O God, Glory to Thee!

O Heavenly King, the Comforter, the Spirit of Truth, Who art everywhere and fillest all things; Treasury of Blessings and Giver of Life; come and abide in us, and cleanse us from every impurity, and save our souls, O Good One.

Holy God, Holy Mighty, Holy Immortal, have mercy on us. \textit{(3x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

O Most Holy Trinity have mercy on us; Lord, cleanse us from our sins; Master, pardon our transgressions; Holy One, visit and heal our infirmities for Thy Name's sake.

Lord, have mercy \textit{(3x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{All:}Our Father, who art in heaven, hallowed be Thy Name.  Thy Kingdom come, Thy will be done, on earth, as it is in heaven.  Give us this day, our daily bread, and forgive us our trespasses as we forgive those who trespass against us; and lead us not into temptation, but deliver us from evil.

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}For Thine is the Kingdom and the power and the glory of the Father, and of the Son, and of the Holy Spirit, now and ever and unto ages of ages.

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}Amen.  Lord, have mercy \textit{(12x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

Come, let us worship God our King, Come, let us worship and fall down before Christ our King and our God, Come, let us worship and fall down before Christ Himself, our King and our God.

\end{hang}

\begin{center}
\textbf{Psalm 50}
\end{center}

\begin{hang}
\input{./input/psalm50}

\end{hang}

\newpage
\begin{center}
\textbf{Psalm 69}
\end{center}

\begin{hang}
\input{./input/psalm69}

\end{hang}

\begin{center}
\textbf{The Lesser Doxology}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}Glory to God in the highest, and on earth peace, good will toward men.

We praise Thee, we bless Thee, we worship Thee, we glorify Thee, we give thanks to Thee for Thy great glory.

O Lord, God, heavenly King, God the Father Almighty! O Lord, the Only-Begotten Son, Jesus Christ, and the Holy Spirit;

O Lord God, Lamb of God, Son of the Father, Who takest away the sin of the world, have mercy on us!  Thou that takest away the sins of the world, receive our prayer.  Thou that sittest at the right hand of God the Father have mercy on us!

For Thou alone art holy, Thou alone art Lord, Thou only, O Jesus Christ, in the glory of God the Father.  Amen.

Every night will I give thanks to Thee and praise Thy Name for ever and ever!

Lord, Thou hast been our refuge from generation to generation!  I said, Lord, have mercy on me, heal my soul, for I have sinned against Thee.  Lord, I flee unto Thee.  Teach me to do Thy will, for Thou art my God.

For with Thee is the fountain of life, and in Thy light shall we see light.  O continue Thy mercy unto those who know Thee!

Vouchsafe, O Lord to keep us this night without sin.  Blessed art Thou, O Lord, God of our Fathers, and praised and glorified is Thy Name forever.  Amen.  Let Thy mercy, O Lord, be upon us, as we have set our hope on Thee.

Blessed art Thou, O Lord, teach me Thy statutes.

Blessed art Thou, O Master, make me to understand Thy commandments.

Blessed art Thou, O Holy One, enlighten me with Thy precepts.

Thy mercy, O Lord, endures forever, despise not the works of Thy hands. To Thee belongs worship, to Thee belongs praise, to Thee belongs glory, to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. 
Amen.

\end{hang}


\begin{center}
\textbf{Creed}
\end{center}


\begin{hang}
\noindent\makebox[\indt][l]{All:}I believe in one God, the Father Almighty, maker of heaven and earth, and of all things, visible and invisible.

And in one Lord, Jesus Christ, the Son of God, the Only-begotten, begotten of the Father before all ages.  Light of Light; True God of True God; begotten, not made; of one essence with the Father, by Whom all things were made; Who for us men and for our salvation came down from heaven, and was incarnate of the Holy Spirit and the Virgin Mary, and became man.  And He was crucified also for us under Pontius Pilate, and suffered, and was buried.  And the third day He rose again, according to the Scriptures, and ascended into heaven, and sits at the right hand of the Father; and He shall come again with glory to judge the living and the dead; Whose Kingdom shall have no end.

And in the Holy Spirit, the Lord, the Giver of Life, Who proceeds from the 
Father; Who with the Father and the Son together is worshipped and glorified; 
Who spoke by the prophets;

In One, Holy, Catholic, and Apostolic Church.  I acknowledge one Baptism for he 
remission of sins.  I look for the resurrection of the dead, and the life of 
the world to come.  Amen.

\end{hang}

\begin{center}
\textbf{Hymn to the Theotokos}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}It is truly meet to bless You, O Theotokos, ever blessed and most pure, and the Mother of our God.  More honorable than the Cherubim, and more glorious beyond compare than the Seraphim: without defilement You gave birth to God the Word: true Theotokos, we magnify You.

\end{hang}

\begin{center}
\textbf{Troparia}
\end{center}

\noindent
\textit{Troparia of the day, then:}
 
\begin{center}
\textbf{Monday}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}The memory of the righteous is celebrated with songs of praise, but the Lord's testimony is sufficient for you, O Forerunner.  You were shown indeed to be the most honorable of the prophets, for in the waters you baptized the One Whom you preached.  After suffering with  joy on behalf of the Truth, you proclaimed even to those in hell the God Who appeared in the flesh, Who takes away the sin of the world and grants us great mercy.

\end{hang}

\begin{center}
\textbf{Tuesday}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{}O Lord, save Thy people and bless Thine inheritance.  Grant victories to the Orthodox Christians over their adversaries; and by virtue of Thy Cross, preserve Thy habitation.

\end{hang}


\begin{center}
\textbf{Wednesday}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{}O Holy Apostles, intercede with our merciful God that He may grant to our souls the forgiveness of our sins.

You appeared to your flock as a rule of faith, an image of humility and a teacher of abstinence.  Because of your lowliness Heaven was opened to you; because of your poverty riches were granted to you.  O Holy Bishop Nicholas, pray to Christ our God to save our souls.

\end{hang}

\begin{center}
\textbf{Thursday}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{}O Lord, save Thy people and bless Thine inheritance.  Grant victories to the Orthodox Christians over their adversaries; and by virtue of Thy Cross, preserve Thy habitation.

\end{hang}

\noindent
\textcolor{red}{\textit{Reader continues immediately:}}

\begin{hang}
\noindent\makebox[\indt][l]{}Have mercy on us, O Lord, have mercy on us, for laying aside all excuse, we sinners offer to Thee, as to our Master, this supplication: Have mercy on us.

Glory to the Father, and to the Son, and to the Holy Spirit:

O Lord, have mercy on us, for in Thee have we put our trust. Do not be angry with us, nor remember our iniquities, but look down on us even now, since Thou art compassionate, and deliver us from our enemies, for Thou art our God and we are Thy people; we are all the work of Thy hands, and we call on Thy Name.

Now and ever, and unto ages of ages.  Amen.

Open to us the doors of compassion, O Blessed Theotokos, for we have set our hope on You; may we not perish, but be delivered from adversity through You, the salvation of the Christian people.

Lord, have mercy. \textit{(12x)}

\end{hang}

\begin{center}
\textbf{Prayer of the Hours}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}Thou who at every season and every hour, in heaven and on earth art worshipped and glorified; O Christ our God, who art long-suffering, merciful and compassionate; who loves the just and shows mercy to those who are hardened in sin; who calls all men to salvation through the promise of blessings to come: do Thou the same Lord, receive our supplications at this present time, and direct our lives according to Thy commandments. Sanctify our souls,  purify our bodies, correct our thoughts, cleanse our minds, and deliver us from all tribulations, evil, and distress. Surround us with Thy holy angels, that guided and guarded by their host, we may attain to the unity of the faith, and to the knowledge of Thine unapproachable glory, for Thou art blessed unto ages of ages. Amen.

Lord, have mercy. \textit{(3x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever, and unto ages of ages.  Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim: without defilement You gave birth to God the Word: true Theotokos, we magnify You.

In the Name of the Lord, bless Father!

\textcolor{red}{\textit{If Bishop is present:}}

In the Name of the Lord, bless Master!

\textcolor{red}{\textit{If Metropolitan is present:}}

In the Name of the Lord, Most Blessed Master, bless!

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}God, be bountiful to us and bless us, show us the light of Thy countenance, and be merciful unto us.

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}Amen.

\end{hang}

\textcolor{red}{\textit{Turning to Icon of Theotokos}}

\begin{center}
\textbf{Prayer to Theotokos}
\end{center} 

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}O all-pure and incorruptible Virgin Bride of God, and our sovereign Lady, who made the Word of God one with mankind by gloriously giving birth to Your Son, and joining our fallen nature to His divine nature; who are the hope of the despairing and the support of those in distress, the swift defender of those who turn to You and the refuge of all Christians; do not turn from me, an unclean sinner, who have destroyed myself with unworthy Thoughts, words and deeds, and been enslaved by forgetfulness to the carnal passions of life; but have compassion on me, O Theotokos, and accept the prayer of a sinner and prodigal, offered from unclean lips.  Exercise Your boldness as a Mother, and pray to Your Son, our Lord and Master, that He will make known to me also His compassionate goodness, and overlooking my countless sins, will turn me to repentance, and make me fervent in doing His commandments.

Be with us always in Your grace and loving mercy, for You are the fervent helper, who turns away the assaults of enemies and guides men towards salvation, caring for my unworthy soul at the hour of death, and driving from it the darkness of evil spirits.  In the Day of Judgment free me from eternal torment, and show me to be an heir of the divine glory of Your Son and our God.

Grant this, O Lady Theotokos, by Your prayers and intercessions, through the mercy and loving-kindness of Your Only-Begotten Son, our Lord and Savior Jesus Christ, to Whom are due all glory, honor, and worship, with the Father Who is eternal, and His All-Holy, Good, and Life-Giving Spirit, now and ever, and unto ages of ages.  Amen.

\end{hang}

\textcolor{red}{\textit{Turning to Icon of Savior:}}

\begin{center}
\textbf{Prayer to Christ}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{}And grant rest, O Master, to our souls and bodies as we sleep; preserve us from the gloomy slumber of sin and from the dark passions of the night. Calm the impulses of carnal desires; quench the fiery darts of the Evil One which are craftily directed against us.  Still the rebellions of the flesh, and put far from us all anxiety and worldly cares. Grant us, O God, a watchful mind, pure thoughts, a sober heart, and a quiet rest, free from every vision of the devil.  Raise us up again at the hour of prayer, strengthened in Thy precepts, and holding within us steadfastly the thought of Thy commandments.  Grant that we may sing praises to Thee through the night, and that we may hymn, bless, and glorify Thine all-honorable and majestic Name, of the Father, and of the Son, and of the Holy Spirit, now and ever, and unto ages of ages.  Amen. 
\end{hang}

\textcolor{red}{\textit{Turning back to Icon of Theotokos:}}

\begin{hang}
\noindent\makebox[\indt][l]{}O exceedingly glorious and ever-virgin Theotokos, bring our petitions before Your Son and our God, and implore Him that through You He will save our souls.  Amen.
\end{hang}

\textcolor{red}{\textit{Turning to face Royal Doors:}}

\begin{hang}
\noindent\makebox[\indt][l]{}O Father, my Hope;  O Son, my Refuge;  O Holy Spirit, my Protection;  O Holy Trinity, glory to Thee!

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}Glory to the Father, and to the Son, and to the Holy Spirit, now and ever, and unto ages of ages.  Amen. Lord, have mercy. \textit{(3x)}

In the Name of the Lord, bless Father!

\textcolor{red}{\textit{If Bishop is present:}}

In the Name of the Lord, bless Master!

\textcolor{red}{\textit{If Metropolitan is present:}}

In the Name of the Lord, Most Blessed Master, bless!

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}O Master, great in mercy, Lord Jesus Christ our God: through the prayers of our All-pure Lady, the Theotokos and ever-virgin Mary; through the might of the precious and life-giving Cross; through the prayers of the honorable Bodiless Powers of Heaven; of the honorable, glorious Prophet, Forerunner, and Baptist, John; of the holy glorious and all-laudable Apostles; of the holy, glorious, and gloriously triumphant martyrs; of our venerable and God-bearing fathers: Basil the Great, Gregory the Theologian and John Chrysostom; of the Enlighteners of North America, our blessed Father Herman of Alaska, Innocent, Tikhon the Confessor of Moscow; Raphael of Brooklyn and the righteous priests Alexis and Jacob; of the holy and righteous Ancestors-of-God, Joachim and Anna, and of all Thy Saints: make our prayer acceptable;  grant unto us remission of our iniquities;  hide us under the shadow of Thy wings;  drive far from us every foe and adversary; give peace to our life;  have mercy upon us and upon Thy world, O Lord, and save our souls, forasmuch as Thou art merciful and lovest mankind.

\end{hang}
\noindent
\textcolor{red}{\textit{Making prostration, priest asks forgiveness of the faithful, who ask forgiveness of him in return:}}

\noindent\makebox[\indt][l]{Priest:}Bless, and forgive me, fathers and brethren:

\noindent\makebox[\indt][l]{People:}God forgives you, Father.

\noindent
\textcolor{red}{\textit{Facing the Royal Doors}}

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}Let us pray for all Orthodox bishops, for our Metropolitan \underline{``          ''}, for the honorable priesthood, the diaconate in Christ, and for all the clergy and the people:

\end{hang}

\noindent\makebox[\indt][l]{People:}Lord, have mercy. \textit{(after each petition)}

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}For this country, its president, its civil 
authorities, and its armed forces everywhere:

For those who hate us and those who love us:

For those who are kind to us and serve us:

For those who have asked us to pray for them, unworthy Though we may be:

For the release of prisoners:

For those who are traveling by land, by sea and by air:

For those who lie sick:

Let us pray also for abundance of the fruits of the earth:

And for every soul of Orthodox Christians departed this life:

For all Orthodox bishops:

For our parents and brethren, and for all departed this life before us, who here and in all the world lie asleep in the Lord:

Let us say also for ourselves!

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{People:}Lord have mercy, Lord have mercy, Lord have 
mercy!

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}Through the prayers of our Holy Fathers, 
Lord Jesus Christ, our God, have mercy on us.

\end{hang}

\noindent\makebox[\indt][l]{People:}Amen.

\noindent
\textcolor{red}{\textit{Priest goes to stand before Icon of in center of temple to give blessings to each of the faithful, before this we sing either Beneath your Compassion or the Troparion of the feast.}}

\noindent
Beneath Your compassion we take refuge, O Theotokos. Despise not our prayer in our necessities, but deliver us from harm, O only pure, only blessed one. Most Holy Theotokos, save us! Most Holy Theotokos, save us! Most Holy Theotokos, save us!