\begin{center}
\addsec{\textsc{\textbf{Post-Communion Prayers}}}
\end{center}

\noindent\makebox[\indt][l]{Reader:}Glory to Thee, our God, glory to Thee! \textit{(3x)}

I thank Thee, O Lord my God, for Thou hast not rejected me, a sinner, but hast made me worthy to be a partaker of Thy Holy Things. I thank Thee, for Thou hast permitted me, the unworthy, to commune of Thy most pure and Heavenly, Gifts. But, O Master Who lovest mankind, Who for our sakes didst die and rise again, and gavest us these awesome and life-creating Mysteries for the good and sanctification of our souls and bodies; let them be for the healing of our soul and body, the repelling of every adversary, the illumining of the eyes of my heart, the peace of my spiritual power, a faith unashamed, a love unfeigned, the fulfilling of wisdom, the observing of Thy commandments, the receiving of Thy divine grace, and the attaining of Thy Kingdom. Preserved by them in Thy holiness, may I always remember Thy grace and live not for myself alone, but for Thee, our Master and Benefactor. May I pass from this life in the hope of eternal life, and so attain to the everlasting rest, where the voice of those who feast is unceasing, and the gladness of those who behold the goodness of Thy countenance is unending. For Thou art the true desire and the ineffable joy of those who love Thee, O Christ our God, and all creation sings Thy praise forever. Amen.

\begin{center}
	\textbf{A Prayer of St. Basil the Great}
\end{center}

O Master, Christ our God, King of the ages, and maker of all things: I thank thee for all the good things which thou hast bestowed upon me, and for this partaking of thine immaculate and life-giving Mysteries. Wherefore I pray thee, who art good and lovest mankind: Keep me under thy protection, and in the shadow of thy wings; and grant unto me with a pure conscience and even unto my last breath, to partake of thy holy Mysteries, unto remission of sins and unto life everlasting. For thou art the Bread of Life, the Fountain of holiness, the Giver of good things, and unto thee we ascribe glory: to the Father, and to the Son, and to the Holy Spirit: now and ever, and unto ages of ages. Amen.


\begin{center}
	\textbf{A Prayer of St. Simon Metaphrastes}
\end{center}

Freely Thou hast given me Thy Body for my Food, O Thou Who art a Fire consuming the unworthy! Consume me not, O my Creator, but instead enter into my members, my reins, my heart! Consume the thorns of my transgressions! Cleanse my soul and sanctify my reasonings! Make firm my knees and body! Illumine my five senses! Nail me to the fear of Thee! Always protect, guard, and keep me from soul destroying words and deeds! Cleanse me, purify me, and adorn me! Give me understanding and illumination! Show me to be a temple of Thy One Spirit, and not the home of many sins! May every evil thing, every carnal passion, flee from me as from a fire as I become Thy tabernacle through Communion! I offer Thee as intercessors all the Saints: the leaders of the Bodiless Hosts, Thy Forerunner, the wise Apostles, and Thy Pure and Blameless Mother! Accept their prayers in Thy love, O my Christ, and make me, Thy servant, a child of light! For Thou art the only Sanctification and Light of our souls, O Good One, and to Thee, our Master and God, we ascribe glory day by day!

\begin{center}
	\textbf{Another Prayer}
\end{center}

May thy holy Body, O Lord Jesus Christ our God, be unto me for life eternal, and thy precious Blood unto remission of my sins. May this Eucharist be unto me for joy, health, and gladness; and at thy dread Second Coming make me, a sinner, worthy to stand at the right hand of thy glory: through the intercessions of thine all-immaculate Mother and of all thy Saints.  Amen.

\begin{center}
	\textbf{A Prayer to the Theotokos}
\end{center}

O  All-holy Lady Theotokos, light of my darkened soul, my hope, my shelter, my refuge, my consolation and my joy: I thank thee that thou hast accounted me worthy, although unworthy, to be a partaker of the immaculate Body and precious Blood of thy Son. But do thou, who gavest birth to the true Light, enlighten the mental eyes of my heart; O thou who didst bear the fountain of immortality, quicken thou me who lie dead in sin, O compassion-loving Mother of the merciful God, have mercy upon me, and grant me humility and contrition of heart, and meekness in my thoughts, and deliverance from the bondage of my vain imaginings. And account me worthy, even unto my last breath, to receive without condemnation the sanctification of the immaculate Mysteries, unto the healing of both soul and body. And grant unto me tears of repentance and confession, that I may hymn thee and glorify thee all the days of my life: for blessed and glorified art thou unto all ages.  Amen.

Lord, now lettest Thou Thy servant depart in peace, according to Thy word! For mine eyes have seen Thy Salvation, which Thou hast prepared before the face of all people: a Light to lighten the Gentiles, and the glory of Thy people, Israel!

Holy God! Holy Mighty! Holy Immortal! Have mercy on us. \textit{(3x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

O most holy Trinity: have mercy on us. Lord: cleanse us from our sins. Master: pardon our transgressions. Holy One: visit and heal our infirmities, for Thy name's sake.

Lord, have mercy. \textit{(3x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

Our Father, who art in heaven, hallowed he Thy name. Thy Kingdom come. Thy will he done, on earth as it is in heaven. Give us this day our daily bread; and forgive us our trespasses, as we forgive those who trespass against us; and lead us not into temptation, but deliver us from the evil one. 

Through the prayers of our Holy Fathers, O Lord Jesus Christ our God, have mercy on us and save us. Amen.