\begin{center}
\addsec{\textsc{\textbf{Pre-Communion Prayers}}}
\end{center}

In the name of the Father and of the Son and of the Holy Spirit. Amen.

\begin{hang}
\noindent\makebox[\indt][l]{Priest:}Blessed is our God, always, now and ever and unto ages of ages.

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Reader:}Amen. Glory to Thee, our God, glory to Thee!

O Heavenly King, the Comforter, the Spirit of Truth who art everywhere and fillest all things. Treasury of Blessings, and Giver of Life: Come and abide in us, and cleanse us from every impurity, and save our souls, O Good One.

Holy God! Holy Mighty! Holy Immortal! Have mercy on us. \textit{(3x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

O most holy Trinity: have mercy on us. Lord: cleanse us from our sins. Master: pardon our transgressions. Holy One: visit and heal our infirmities, for Thy name's sake.

Lord, have mercy. \textit{(3x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

Our Father, who art in heaven, hallowed he Thy name. Thy Kingdom come. Thy will he done, on earth as it is in heaven. Give us this day our daily bread; and forgive us our trespasses, as we forgive those who trespass against us; and lead us not into temptation, but deliver us from the evil one. 

Lord, have mercy. \textit{(12x)}

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

Come, let us worship God our King!

Come, let us worship and fall down before Christ, our King and our God!

Come, let us worship and fall down before Christ Himself, our King and our God!

\end{hang}

\begin{center}
	\textbf{Psalm 22 (23)}
\end{center}

The Lord is my shepherd, I shall not want; He maketh me to lie down in green pastures. He leadeth me beside the still waters; He restoreth my soul! He leadeth me in the paths of righteousness for His name's sake.

Yea though I walk through the valley of the shadow of death I will fear no evil; For Thou art with me; Thy rod and Thy staff, they comfort me. Thou preparest a Table before me in the presence of mine enemies; Thou anointest my head with oil; my cup runneth over! Surely goodness and mercy shall follow me all the days of my life; and I shall dwell in the house of the Lord forever.


\begin{center}
	\textbf{Psalm 23 (24)}
\end{center}

The earth is the Lord's and the fullness thereof, the world and those who dwell therein; for He has founded it upon the seas, and established it upon the rivers. Who shall ascend the hill of the Lord? And who shall stand in His holy place? He who has clean hands and a pure heart, who does not lift up his soul to what is false, and does not swear deceitfully. He will receive blessing from the Lord, and vindication from the God of his salvation. Such is the generation of those who seek Him, who seek the face of the God of Jacob. Lift up your heads, O gates! and be lifted up, O ancient doors! that the King of glory may come in. Who is the King of glory? The Lord, strong and mighty, the Lord, mighty in battle! Lift up your heads, O gates! and be lifted up, O ancient doors! that the King of glory may come in. Who is this King of glory? The Lord of hosts, He is the King of glory!


\begin{center}
	\textbf{Psalm 115 (116)}
\end{center}

I kept my faith, even when I said, ``I am greatly afflicted''; I said in my consternation, ``Every man is a liar.'' What shall I render to the Lord for all His bounty to me? I will lift up the Cup of Salvation and call on the name of the Lord, I will pay my vows to the Lord in the presence of His people. Precious in the sight of the Lord is the death of His saints. O Lord, I am Thy servant; I am Thy servant, the son of Thy handmaid. Thou hast loosed my bonds. I will offer to Thee the Sacrifice of Thanksgiving and call on the name of the Lord. I will pay my vows to the Lord in the presence of all His people, in the courts of the house of the Lord, in your midst O Jerusalem!


\textcolor{red}{\textit{And the following Troparia, Tone 8:}}

Disregard my iniquities, O Lord Who wast born of Virgin! Cleanse my heart and make it a temple of Thy most pure Body and Blood. Turn me not away from Thy countenance, for Thy great mercy is immeasurable.

Glory to the Father, and to the Son, and to the Holy Spirit: 

How dare I partake of Thy Holiness in my unworthiness? Even if I dare to approach Thee with the worthy, my garment accuses me, for it is not a wedding-garment, and I secure the condemnation of my most sinful soul. Cleanse, O Lord, the defilement of my soul and save me, for Thou lovest mankind.

Now and ever and unto ages of ages. Amen.

Great is the multitude of my sins, O Theotokos! I come to you, O Pure One, in need of salvation. Visit my ailing soul, O you who alone are blessed, and pray to your Son and our God that He absolve the evil I have done.


\textcolor{red}{\textit{If the Canon of Preparation for Holy Communion has not been read the preceding evening, it may be read here.}}

\begin{center}
\textit{Canon in preparation for Holy Communion}
\end{center}

\begin{center}
\textbf{Ode 1 (Tone 2)}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Irmos:}Come, O People, let us sing a hymn to Christ God, Who divided the sea and guided the people Whom He led out of the bondage of Egypt, for He has glorified Himself.

Create in me a clean heart, O God, and put a new and right spirit within me.

May Thy Holy Body and Precious Blood, O Lord, be my Bread of everlasting life, healing me of various afflictions.

Cast me not away from Thy presence, and take not Thy Holy Spirit from me. 

Make me worthy to partake of Thy most pure Body and Divine Blood, O Christ, for I am unworthy and accursed, defiled by unseemly deeds.

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

Thou art the good soil, blessed Bride of God, which bore the ear of grain, the Savior of the world, which sprang from thy untilled field. Grant that I may be saved by eating it.

\end{hang}

\begin{center}
\textbf{Ode 3}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Irmos:}Having established me on the rock of faith, Thou hast strengthened me against my enemies. My spirit rejoices when I sing:

There is none holy as our God, and none more righteous than Thou, O Lord!

Create in me a clean heart, O God, and put a new and right spirit within me.

Give me tears, O Christ, to cleanse the filth from my heart. Then, cleansed and with a good conscience, may I come with fear and faith to partake of Thy Divine Gifts, O Master.

Cast me not away from Thy presence, and take not Thy Holy Spirit from me.

O Lover of mankind, may Thy most pure Body and Divine Blood be for the remission of my sins, the communion of the Holy Spirit, life everlasting, and estrangement from passions and sorrows.

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

Most holy Table of the Heavenly Bread which mercifully came down from on high, giving new life to the world; grant that I, who am unworthy, may now taste of Him in fear and live! 

\end{hang}

\begin{hang}
\noindent\makebox[\indt][l]{Irmos:}Thou didst not come as an emissary or an angel, Lord, but from a Virgin, taking flesh and saving the fullness of my humanity. I therefore call out to Thee: Glory to Thy power, O Lord!

Create in me a clean heart, a God, and put a new and right spirit within me.

Because of human sins, Thou didst will to be slaughtered like a lamb, Most Merciful One Who wast incarnate for us. I pray, therefore: cleanse my sins as well.

Cast me not away from Thy presence, and take not Thy Holy Spirit from me. Heal the wounds of my soul, Lord, and fully sanctify me. Grant, Master, that I, who am wretched, may partake of Thy Divine Mystical Supper.

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

Incline towards me, O Lady, the One Who came from thy womb. Keep me, thy servant, undefiled and spotless, that I may be sanctified by receiving the spiritual pearl.

\end{hang}

\begin{center}
	\textbf{Kontakion, Tone 2}
\end{center}

Do not judge me unworthy to receive Thy Body and Divine Blood at this time. May the communion of Thy most pure and dread Mysteries not be to my condemnation, though I am wretched. Be it rather, for eternal and everlasting life.

\begin{center}
	\textbf{Ode 7}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Irmos:}The most wise youths would not serve the golden idol, but walked into the flames themselves, scorning the pagan gods. They sang amid the flames and an Angel bedewed them with the words: The prayer of your lips has been heard.

Create in me a clean heart, O God, and put a new and right spirit within me.

May this communion of Thine immortal Mysteries, the fountain of good, O Christ, be my light, my life, and my dispassion. May it lead to progress and the increase of divine virtues, only Good One, that I may glorify Thee.

Cast me not away from Thy presence, and take not Thy Holy Spirit from me.

As I draw near to Thine immortal and divine Mysteries with love and trembling, may I be delivered from passions, enemies, want, and every sorrow. Grant that I may sing to Thee: blessed art Thou, Lord God of our fathers.

Glory to the Father, and to the Son, and to the Holy Spirit, now and ever and unto ages of ages. Amen.

To thee who are full of the Grace of God and bore Christ the Savior beyond understanding, I thy servant pray -- the impure praying to the Pure One: cleanse me, who now wish to draw near to the most pure Mysteries, from all defilement of flesh and spirit.

\end{hang}

\begin{center}
	\textbf{Ode 8}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Irmos:}God came down upon the Hebrew youths in the fiery furnace and changed the flames into dew. Praise the acts of the Lord, and exalt Him throughout all ages!

Create in me a clean heart, O God, and put a new and right spirit within me.

O God, my Savior, allow me in my present despair to be a partaker of Thy heavenly, awesome, and holy Mysteries and of Thy divine and mystical supper, O Christ.

Cast me not away from Thy presence, and take not Thy Holy Spirit from me. Having run to Thy kindness, O Good One, I cry out to Thee in fear: be in me and I in Thee, as Thou didst say, O Savior! Behold: emboldened by Thy mercy, I eat Thy Flesh and drink Thy Blood.

Let us bless the Father, and the Son, and the Holy Spirit, the Lord; now and ever and unto ages of ages. Amen.

I tremble when I partake of fire, for fear that I might burn like wax or grass. O the awesome Mysteries! O the kind-heartedness of God! How can I, who am clay, commune of the Divine Body and Blood and become incorruptible?

\end{hang}

\begin{center}
	\textbf{Ode 9}
\end{center}

\begin{hang}
\noindent\makebox[\indt][l]{Irmos:}Our God and Lord, the Son of the Eternal Father, revealed Himself to us. He was incarnate of a Virgin that He might enlighten those in darkness and gather those who were scattered. We therefore magnify the all--hymned Theotokos.

Create in me a clean heart, O God, and put a new and right spirit within me.

Taste and see that this is Christ, the Lord Who of old became like us for us and Who, having once offered Himself as an offering to His Father, is forever immolated, sanctifying communicants.

Cast me not away from Thy presence, and take not Thy Holy Spirit from me.

May I be sanctified in soul and body, Master! May I be enlightened! May I be saved! May I become Thy dwelling through communion of the Sacred Mysteries, having Thee living in me with the Father and the Spirit, O Most Merciful Benefactor!

Glory to the Father, and to the Son, and to the Holy Spirit.

May Thy Body and Most Pure Blood, my Savior, be to me as fire and light. May they set flame to my sinful matter, burning the thorns of passions and fully I enlightening me to worship Thy Divinity.

Now and ever and unto ages of ages. Amen.

God took flesh of thy pure blood. Every race therefore hymns thee, O Theotokos, and the intelligent multitudes glorify thee, for through thee we beheld the Ruler of all becoming substance in humanity.

Lord, have mercy. \textit{(40x)}

\end{hang}

\textcolor{red}{\textit{The above are said with as many prostrations as desired. Then we read the following Verses of Instruction:}}

When you intend, O man, to eat the Master's Body, approach with fear, lest you be burned -- for It is fire! Before drinking the Divine Blood in Communion, make peace with those who have grieved you. Only then
may you dare to eat the Mystical Food. Before partaking of the Dread Sacrifice, the life-giving Body of the Master, pray, trembling, in this manner: 

\begin{center}
\textbf{1st Prayer: of St. Basil the Great}
\end{center}

O Lord and Master, Jesus Christ our God, the Fountain of life and immortality, the Creator of everything visible and invisible, the eternal and everlasting Son of the eternal Father: Thou hast come in these latter days because of the abundance of Thy goodness. Thou hast put on our human flesh and wast crucified and buried for us thankless and graceless men, and through Thine own blood Thou hast renewed our human nature which is corrupted by sin. And now, O Immortal King, accept the repentance of me a sinner, and incline Thine ear to me and listen to my words: 

I have sinned, O Lord, I have sinned before heaven and before Thy face, and I am not worthy to look upon the height of Thy Glory. I have provoked Thy goodness, I have transgressed Thy commandments, I have not obeyed Thy statutes. But, O Lord, since Thou dost not remember evil, but art long-suffering and of great mercy, Thou hast not given me over to destruction for my lawlessness, but hast ever awaited my conversion. 

O Lover of mankind, Thou hast said by Thy prophets: ``I have no pleasure in the death of the wicked, but that the wicked turn from his way and live.'' For Thou dost not wish, O Master, that the work of Thy hands should perish, neither dost Thou take pleasure in the destruction of men, but Thou desirest that all men should be saved and come to the knowledge of the truth. 

Therefore, although I am unworthy both of heaven and of earth and of this passing life, having wholly yielded myself to sin and defiled Thine image, yet being Thy creature and of Thy making, I do not despair of my salvation in my wickedness. But made bold by Thine infinite compassion, I draw near.

Receive me, O Christ Who lovest mankind, as Thou didst receive the prostitute, the thief, the tax-collector and the prodigal. Take away the heavy burden of my sins, for Thou takest away the sins of the world. Thou healest the infirmities of mankind. Thou callest to Thyself and givest rest to those who labor and are heavy laden. 

Thou hast not come to call the righteous, but sinners to repentance. Cleanse me from every stain of flesh and spirit. Teach me to fulfill holiness in fear of Thee, that having the testimony of my own conscience clean, and having communion of Thy holy things, I may be united with Thy Body and Blood and may have Thee to dwell and abide in me, with the Father and Thy Holy Spirit. 

O Lord Jesus Christ my God, may the communion of Thy most pure and life-creating mysteries not bring me into judgment, nor may I become weak in soul and body by partaking in an unworthy manner, but grant me to receive communion of Thy holy things without condemnation even to my very last breath, and by them to receive communion of the Holy Spirit, provision for the journey of eternal life, and an acceptable answer at Thy dread judgment seat; that I, together with all Thy chosen ones, may also be a partaker of the incorruptible blessings which Thou hast pre pared for those who love Thee, O Lord, in whom Thou art glorified forever. Amen.

\begin{center}
\textbf{2nd Prayer: of St. John Chrysostom}
\end{center}

O Lord my God, I know that I am not worthy nor sufficiently pleasing that Thou shouldst come under the roof of the house of my soul, for it is entirely desolate and fallen in ruin, and Thou wilt not find in me a place worthy to lay Thy head. But as Thou didst humble Thyself from on high for our sake, so now humble Thyself to my lowliness. 

As Thou didst deign to lie in a cavern, in a manger of dumb beasts, so now deign to enter into the manger of my beastly soul, and into my soiled body.

As Thou didst not disdain to enter and to eat with sinners in the house of Simon the leper, so now be pleased to enter into the house of my soul, humble and leprous and sinful.

As Thou didst not cast away the sinful woman who came to touch Thee, so have compassion on me a sinner who comes to touch Thee. As Thou didst not abhor the kiss of her sin-stained and unclean mouth, do not abhor my mouth, worse stained and more unclean than hers, nor my stained and shamed and unclean lips, nor my still more impure tongue.

But let the fiery coal of Thy most pure Body and Thy most precious Blood bring me sanctification, enlightenment and strengthening of my lowly soul and body, relief from the burden of my many transgressions, protection against every action of the devil, repulsion and victory over my wicked and evil habits, mortification of my passions, accomplishment of Thy commandments, increase of Thy divine grace, and inheritance of Thy Kingdom. For I do not come to Thee in presumption, O Christ my God, but made bold by Thine inexpressible goodness, lest I stray far away from Thy flock, O Master, and become caught by the wolf of souls.

Therefore, I pray Thee, O Master, for Thou alone art holy: sanctify my soul and body, my mind and heart, my muscles and bones. Renew me entirely. Implant Thy fear in my fleshly members and let Thy sanctification never be removed from me. 

Be my helper and defender, guide my life in peace and make me worthy to stand at Thy right hand with all Thy saints.

By the prayers and supplications of Thy most pure Mother, of Thy spiritual servants, the most pure angelic powers, and of all the saints who have been well-pleasing to Thee. Amen. 

\begin{center}
	\textbf{3rd Prayer: of St. Simeon Metaphrastes}
\end{center}

O only pure and incorruptible Lord! Because of the inexpressible mercy of Thy love for mankind, Thou didst take to Thyself our entire human composition from the pure blood of the Virgin who gave birth to Thee beyond nature, by the descent of the Holy Spirit and the goodwill of the ever-existing Father.

O Christ Jesus, Wisdom of God and Peace and Power, through the human nature which Thou didst take to Thyself, Thou didst suffer the life-creating and saving passion: the Cross, the nails, the spear -- death itself. Put to death in me the soul-destroying passions of the body. 

Through Thy burial Thou didst capture the kingdom of death. Bury in me the evil devices of the devil with good thoughts, and destroy the spirits of evil.

Through Thy life-bringing Resurrection Thou didst raise up the first father who had fallen. Raise me up who am sunk down in sin and give me the image of repentance.

Through Thy glorious Ascension Thou didst deify the flesh which Thou didst assume, and placed it on the throne at the Father's right hand. Grant me to receive a place at the right hand with the saved through communion of Thy holy mysteries.

Through the coming of Thy Spirit, the Comforter, Thou didst make Thy consecrated disciples to be honorable vessels. Show me also to be the receptacle of His coming. 

Thou hast promised to come again to judge the world in righteousness. Grant that I may go to meet Thee in the clouds, my Judge and Creator, with all Thy saints; that I may glorify and praise Thee without end, together with Thy Father Who is without beginning, and Thy most holy and good and life-creating Spirit, now and ever and unto ages of ages. Amen. 

\begin{center}
	\textbf{4th Prayer: of St. John of Damascus}
\end{center}

O Lord and Master Jesus Christ our God, Who alone hast power to absolve men from their sins, for Thou art good and lovest mankind: forgive all my transgressions done in knowledge or in ignorance, and make me worthy without condemnation to have communion of Thy divine, glorious, pure and life-creating mysteries. Let them not be for my punishment, or for the increase of my sins. But let them be for my purification and sanctification, as a promise of the life and Kingdom to come, a defense and a help and a repulsion of every attacker and the removal of my many transgressions. For Thou art a God of mercy and generosity and love for mankind, and to Thee we ascribe glory, with the Father and the Holy Spirit, now and ever and unto ages of ages. Amen.  

\begin{center}
	\textbf{5th Prayer: of St. Basil the Great}
\end{center}

I know, O Lord, that I have communion unworthily of Thy most pure Body and Thy most precious Blood, and that I am guilty and drink condemnation to myself not discerning Thy Body and Blood, O my Christ and God. But daring upon Thy generous loving-kindness I come to Thee Who hast said: "He who eats My flesh and drinks My blood abides in Me and I in him." 

Be merciful, therefore, O Lord, and do not rebuke me, a sinner, but deal with me according to Thy mercy, and let Thy holy things be for my purification and healing, for enlightenment and protection, for the repulsion of every tempting thought and action of the devil which works spiritually in my fleshly members. Let them he for boldness and love for Thee, for the correction and grounding of my life, for the increase of virtue and perfection, for the fulfillment of Thy commandments, for the communion of the Holy Spirit, for the journey of eternal life, for a good and acceptable answer at Thy dread judgment, but not for judgment or condemnation. Amen. 

\begin{center}
	\textbf{6th Prayer: of St. Simeon the New Theologian}
\end{center}

From lips defiled and a vile heart, from an impure tongue and a soul defiled, receive my prayer, O my Christ, and do not despise my words, my appearance, nor my shamelessness. Grant me the boldness, my Christ, to say what I desire. Even more teach me what to do and say. I have sinned more than the harlot who, on learning where Thou wast, brought myrrh and came boldly to anoint Thy feet, my God, my Master and my Christ. As Thou didst not turn her away when she came with her heart, so, O Word, turn me not away, but give me Thy feet to hold, to kiss, and to anoint boldly with a stream of tears as a precious ointment. Wash me with my tears, O Word, and cleanse me with them! Remit my transgressions and grant me forgiveness.

Thou knowest the multitude of my evil: Thou knowest also my wounds! Thou seest my scars: Thou knowest also my faith! Thou seest my intentions and hearest my sighs. Nothing is hidden from Thee, myGod, my Maker, my Redeemer -- not even a tear-drop or part of that drop. Thine eyes have seen that which I have not yet done. Thou hast inscribed in Thy book things yet to happen.

See my humility! See each of my labors and all of my sins! Absolve me, O God of all, that with a pure heart, trembling thoughts and a contrite soul I may partake of Thine undefiled and most holy Mysteries which enliven and deify all who partake of them with a pure heart.

Thou hast said, O Master: ``Whoever eats My Body and drinks My Blood abides in Me and I in him!'' True is every word of my Master and God! When I partake of Thy divine and deifying Grace, I am no longer alone -- I am with Thee, my Christ, the Light of the Triple Sun which enlightens the world. May I not remain alone, without Thee, O Lifegiver, my Breath, my Life and my Joy, the salvation of the world. I approach Thee, therefore, with tears, as Thou seest, and a contrite soul. I beg to receive deliverance from my sins. May I partake uncondemned of Thy life-giving and spotless Mysteries, that Thou mayest abide, as Thou hast said, with me, the thrice-wretched.

May the Tempter not find me without Thy Grace and seize me deceitfully, and lead me, deceived, from Thy deifying words. Therefore, I fall down before Thee and fervently cry: As Thou didst receive the Prodigal and the harlot who came to Thee, O Gracious One, receive me, prodigal and defiled.

With a contrite soul I approach Thee now. I know, O Savior, that no one has sinned against Thee as I have, nor done the deeds that I have done. But I also know that neither the greatness of my transgressions, nor the multitude of my sins surpass the great patience of my God and His extreme love for mankind. Through Thy merciful compassion Thou dost cleanse and brighten those who repent with fervor, making them partakers of Light and full communicants of Thy Divinity. To the astonishment of angels and human minds, Thou dost converse with them often as with Thy true friends. This makes me bold, my Christ, this gives me wings! Emboldened by the wealth of Thy generosity towards us, with both joy and trepidation, I who am grass partake of fire. O strange wonder! I am sprinkled with dew and am not burned, as the bush burned of old without being consumed. With grateful thoughts and a grateful heart, with my grateful members, my soul and my body, I now fall down and worship and glorify Thee, my God, for blessed art Thou, now and forever.

\begin{center}
	\textbf{7th Prayer: of St. John Chrysostom}
\end{center}

O God, absolve, remit and pardon me my transgressions -- as many sins as I have committed by word or action or thought, willingly or unwillingly, consciously or unconsciously; forgive me everything since Thou art good and lovest mankind. And by the prayers of Thy most pure Mother, of Thy spiritual servants, the holy angelic powers and all the saints, who from all ages have been well-pleasing to Thee, be pleased to allow me to receive Thy most pure Body and Thy most precious Blood for the healing of my soul and body, and the purification of my evil thoughts. For Thine is the Kingdom and the power and the glory with the Father and the Holy Spirit, now and ever and unto ages of ages. Amen.

\begin{center}
	\textbf{8th Prayer of St. John Chrysostom}
\end{center}

I am not worthy, Master and Lord, that Thou shouldst enter under the roof of my soul; yet inasmuch as Thou desirest to live in me as the Lover of mankind, I approach with boldness. Thou hast commanded: Let the doors be opened which Thou alone hast made and Thou shalt enter with Thy love for mankind just as Thou art. Thou shalt enter and enlighten my darkened reasoning. I believe that Thou wilt do this. For Thou didst not cast away the prostitute who came to Thee with tears, neither didst Thou turn away the tax-collector who repented, nor didst Thou reject the thief who acknowledged Thy Kingdom, nor didst Thou forsake the repentant persecutor, the Apostle Paul, even as he was. But all who came to Thee in repentance Thou didst unite to the ranks of Thy friends, Who alone art blessed forever, now and unto the endless ages. 

\begin{center}
	\textbf{9th Prayer of St. John Chrysostom}
\end{center}

O Lord Jesus Christ my God, absolve, loose, cleanse and forgive me Thy sinful and useless and unworthy servant my errors, transgressions and sinful failings -- as many as I have committed from my youth up to this present day and hour, consciously and unconsciously, in words or actions or reasonings, thoughts, pursuits and in all my senses. By the prayers of Thy Mother the most pure and ever-virgin Mary who gave birth to Thee without human seed, my only hope which will not put me to shame, my intercessor and salvation, grant me to have communion without condemnation of Thy most pure, immortal, life-creating and awesome mysteries; for the remission of sins and unto life everlasting; for sanctification, enlightenment, strength, healing and health of soul and body; for the most perfect removal and destruction of my evil thoughts and reasonings and intentions, fantasies by night, brought by dark and evil spirits; for Thine is the Kingdom and the power and the glory and the honor and the worship, with the Father and Thy Holy Spirit, now and ever and unto ages of ages. Amen. 

\begin{center}
	\textbf{10th Prayer: of St. John of Damascus}
\end{center}

I stand before the doors of Thy temple, and I do not forsake my wicked thoughts. But, O Christ my God, as Thou hast justified the tax-collector, and hast had mercy on the woman of Canaan and hast opened the gates of paradise to the thief, open to me the interior depths of Thy love for mankind and receive me as I come and repent before Thee. Receive me as Thou didst receive the sinful woman and the woman with the flow of blood. For the first embraced Thy most pure feet and received the forgiveness of her sins, and the second just touched the hem of Thy garment and received healing. But I who am lost, daring to receive Thy whole Body, may I not be burned; but receive me as Thou hast received them, and enlighten my spiritual senses, burning up my spiritual faults by the prayers of her who gave birth to Thee without human seed, and of the heavenly angelic powers, for Thou art blessed unto ages of ages. Amen.

\begin{center}
	\textbf{Another Prayer of St. John Chrysostom}
\end{center}

I believe, O Lord, and I confess that Thou art truly the Christ, the Son of the living God, Who camest into the world to save sinners, of whom I am first. I believe also that this is truly Thine own most pure Body, and that this is truly Thine own precious Blood. Therefore, I pray Thee: have mercy upon me and forgive my transgressions both voluntary and involuntary, of word and of deed, committed in knowledge or in ignorance. And make me worthy to partake without condemnation of Thy most pure Mysteries, for the remission of my sins, and unto life everlasting. Amen. 

\textcolor{red}{\textit{As you approach to partake, say silently the following verses of Metaphrastes:}}

Behold: I draw near to the Divine Communion. Burn me not as I partake, O Creator, for Thou art a Fire which burns the unworthy. Rather, cleanse me of all defilement. Of Thy Mystical Supper, O Son of God, accept me this day as a communicant; for I will not speak of Thy Mystery to Thine enemies, neither like Judas will I give Thee a kiss; but like the thief will I confess Thee: Remember me, O Lord, in Thy Kingdom.

\textcolor{red}{\textit{And the following verses:}}

Be awed, O man, when you see the deifying Blood! It is a fire which burns the unworthy! The Divine Body both deifies and nourishes me. It deifies the spirit and wondrously nourishes the mind.

\textcolor{red}{\textit{Then the following Troparia:}}
With love hast Thou drawn me, O Christ, and with Thy divine love hast Thou changed me. Burn away my sins with a spiritual fire and satisfy me with joy in Thee, that I may joyfully magnify Thy two comings, O Good One. How shall I, who am unworthy, enter into the radiance of Thy saints? If I dare to enter the bridal-chamber, my garment accuses me, for it is not a wedding garment, and the angels will bind me and cast me out. Cleanse, O Lord, the filth of my soul and save me, for Thou lovest mankind.

\textcolor{red}{\textit{And this prayer:}}

O Master Who lovest mankind! O Lord Jesus Christ my God! May these holy things not be to my condemnation, though I am unworthy of them. May they be for the cleansing and sanctification of my soul and body and a pledge of the life and Kingdom that are to come.

It is good for me to cleave to God and to place in the Lord the hope of my salvation. Then repeat:

Of Thy Mystical Supper, O Son of God, accept me this day as a communicant; for I will not speak of Thy Mystery to Thine enemies, neither like Judas will I give Thee a kiss; but like the thief will I confess Thee: Remember me, O Lord, in Thy Kingdom.