Have mercy on me, O God, according to Your steadfast love; according to Your abundant mercy blot out my transgressions.

Wash me thoroughly from my iniquity and cleanse me from my sin! For I know my transgressions and my sin is ever before me.

Against You, You only have I sinned, and done that which is evil in Your sight, so that You are justified in Your sentence and blameless in Your judgment.

Behold, I was brought forth in iniquity and in sin did my mother conceive me. Behold, You desire truth in the inward being; therefore teach me wisdom in my secret heart.

Purge me with hyssop and I shall be clean, wash me and I shall be whiter than snow.  Fill me with joy and gladness, let the bones which You have broken	rejoice.  Hide Your face from my sins, and blot out all my iniquities.

Create in me a clean heart, O God, and put a new and right spirit within me. Cast me not away from Your presence, and take not Your Holy Spirit from me.

Restore to me the joy of Your salvation, and uphold me with a willing spirit. Then I will teach transgressors Your ways, and sinners will return to You.

Deliver me from bloodguiltiness, O God, The God of my salvation, and my tongue will sing aloud of Your deliverance.

O Lord, open my lips, and my mouth shall show forth Your praise.  For You have no delight in sacrifice; were I to give a burnt offering, You would not be pleased. The sacrifice acceptable to God is a broken spirit, a broken and contrite heart You will not despise.

Do good to Zion in Your good pleasure; rebuild the walls of Jerusalem, then will You delight in right sacrifices, in burnt offerings and whole burnt offerings; then bulls will be offered on Your altar.