\noindent\makebox[\indt][l]{Reader:}Have mercy on me, O God, according to your great mercy, and according to the fullness of to your compassions blot out my transgression. More thoroughly wash me from my lawlessness, and cleanse me from my sin. For I do know my lawlessness, and my sin is ever before me. Against you only I haye sinned and have done the evil before you, so that you are righteous in your words and conquer in your judging. For, behold, in iniquities I was conceived, and in sins my mother bore me. For, behold, you have loved truth, the unseen and hidden things of your wisdom you have shown me. You will sprinkle me with hyssop and I will be cleansed; you will wash me, and I will be made whiter than snow. You will make me hear joy and gladness; the humbled bones will rejoice. Turn away your face from my sins, and blot out all my iniquities. Create a clean heart in me, O God, and renew a right Spirit in my inward parts. Do not cast me away from your Face, and do not take your Holy Spirit from me. Give me back the joy of your salvation, and make me steadfast with a governing Spirit. I will teach the lawless your ways, and the impious will turn around to you. Deliver me from blood, O God, God of my salvation, and my tongue will rejoice in your righteousness. Lord, you will open my lips, and my mouth will proclaim your praise. For if you had willed a sacrifice, I would have given it, you will not well-will whole burnt offerings. A sacrifice to God is a shattered spirit; a shattered and humbled heart God will not despise. Do good, Lord, to Zion in your good pleasure and the walls of Jerusalem be rebuilt. Then you will well-will sacrifice of righteousness, offering and whole burnt offerings. Then they will offer calves upon your altar.