\documentclass[10pt,letterpaper]{letter}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document} 
Lord, thou hast been our refuge in all generations. Before the mountains existed, and \textit{before} the earth and the world were formed, even from age to age, Thou art. Turn not man back to \textit{his} low place, whereas thou saidst, Return, ye sons of men? For a thousand years in thy sight are as the yesterday which is past, and as a watch in the night. Years shall be vanity to them: let the morning pass away as grass. In the morning let it flower, and pass away: in the evening let it droop, let it be withered and dried up. For we have perished in thine anger, and in thy wrath we have been troubled. Thou hast set our transgressions before thee: our age is in the light of thy countenance. For all our days are gone, and we have passed away in thy wrath: our years have spun out their tale as a spider. \textit{As for} the days of our years, in them are seventy years; and if \textit{men should be} in strength, eighty years: and the greater part of them would be labour and trouble; for weakness overtakes us, and we shall be chastened. Who knows the power of thy wrath? and \textit{who knows how} to number \textit{his days} because of the fear of thy wrath? So manifest thy right hand, and those that are instructed in wisdom in the heart.\\

\noindent
Return, O Lord, how long? and be intreated concerning thy servants. We have been satisfied in the morning with thy mercy; and we did exult and rejoice: let us rejoice in all our days, in return for the days wherein thou didst afflict us, the years wherein we saw evil. And look upon thy servants, and upon thy works; and guide their children. And let the brightness of the Lord our God be upon us: and do thou direct for us the works of our hands.
\end{document}